### 2023-10-28 doc/Thesis/chapter/04-experimental.tex
finish todos

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals, substrates, experimental procedures and any used
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
\td{The experiments can be split into three sections: }
In the first section the base recipe and the base process were sought. 
In the pre-optimization section the boundaries for the optimization were investigated. 
And during the third and final step the experiments for the optimization were performed.
\section{Substrate Preparation}
%\ds{
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5})\ds{ from Sigma Aldrich, thinner}, 
squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%}
\ds{
Four different substrates were used throughout this work: 
microscope glass slides, \gls{ito} glass plates, \gls{fto} glass plates and steel foil provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
}
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

@@

@@

\begin{figure}[hbt]
    \centering
    \begin{circuitikz} \draw
        (0,0) to[european voltage source] (0,2)
        to[ammeter] (2,2) 
        to[generic,l=W] (4,2) 
        to[generic,l=Au] (6,2) 
        to[generic,l=Al] (8,2)
        -- (8,2)
        to[generic,l=ZrO$_2$] (8,0)
        -- (8,0)
        to[generic,l=steel] (6,0)
        to[generic,l=Ag] (4,0)
        to[generic,l=Au] (2,0) 
        to[generic,l=W] (0,0) 
            ;
    \end{circuitikz}
    \caption{Sketch of circuit, from the source clockwise: varibale voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
    \label{fig:circuit}
\end{figure}

@@

The main part of all samples (around 90\%) were pre-optimization samples, 

@@

The \td{glass plate of the film applicator was therefore exchanged with a metal plate which}

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilization agent was changed from \gls{acoh} to 
\gls{ipo} because of much better solution stability.
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent 
showed comparable passivization results and better stability of the solution. 
Therefore \gls{ipo} was used  as stabilzier in further experiments.
\td{After the boundaries of the solution were fixed }
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
\td{See} table \ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% EXPERIMENTAL %%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section the used chemicals, substrates, experimental procedures and any used
equipment are described. 
%\td{Also, the long, exhaustive path to the base solution is described}
%\td{The experiments can be split into three sections: }
First, the base recipe and the base process settings were explored. 
Then, the analysis of samples is discussed and the boundaries for the optimization were investigated during pre-optimization.
Finally, the experiments for the optimization were performed.

\section{Substrate Preparation}
%\ds{
Five different substrates were used throughout this work: 
microscope glass slides 
\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5})\ds{ from Sigma Aldrich, thinner}, 
squared glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{ito} glass plates (\cm{2.5}\x\cm{2.5})\ds{ from Sigma Aldrich}, 
\gls{fto} glass plates (\cm{5}\x\cm{5})\ds{ from Sigma Aldrich} and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%}
\ds{
Four different substrates were used throughout this work: 
microscope glass slides, \gls{ito} glass plates, \gls{fto} glass plates and steel foil provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
}
%
Glass was used because of its availability and to measure transmission and reflectance 
spectra. \gls{fto} and \gls{ito} were used in order to have a conducting substrate, which
is needed to measure the conductivity of the applied layer and for \gls{sem} micrographs.
The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a sonic bath
	\item \minutes{15} in \gls{water} in a sonic bath
	\item \minutes{15} in \gls{ipo} in a sonic bath 
\end{enumerate}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the doctor blading step.

@@

\begin{figure}[htb]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-1.png}
		\caption{}
		\label{fig:micro1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=.8\textwidth]{Pics/micro-2.png}
		\caption{}
		\label{fig:micro2}
	\end{subfigure}
	\begin{subfigure}{\textwidth}
		\centering
		\begin{circuitikz} \draw
			(0,0) to[european voltage source] (0,2)
			to[ammeter] (2,2) 
			to[generic,l=W] (4,2) 
			to[generic,l=Au] (6,2) 
			to[generic,l=Al] (8,2)
			-- (8,2)
			to[generic,l=ZrO$_2$] (8,0)
			-- (8,0)
			to[generic,l=steel] (6,0)
			to[generic,l=Ag] (4,0)
			to[generic,l=Au] (2,0) 
			to[generic,l=W] (0,0) 
				;
		\end{circuitikz}
		\caption{}
		\label{fig:circuit}
	\end{subfigure}
	\caption{View of a sample through the microscope attached to the multimeter and sketch of circuit. 
	\label{fig:micro}
	(a) Sputtered silver contacts on sample with gilded wolfram contact probe touching one of the contacts. 
	(b) Edge of a sample with the probe touching silver paste on top of a sanded patch.
	(c) From the source clockwise: variable voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
\end{figure}

@@

\iffalse
\begin{figure}[hbt]
    \centering
    \begin{circuitikz} \draw
        (0,0) to[european voltage source] (0,2)
        to[ammeter] (2,2) 
        to[generic,l=W] (4,2) 
        to[generic,l=Au] (6,2) 
        to[generic,l=Al] (8,2)
        -- (8,2)
        to[generic,l=ZrO$_2$] (8,0)
        -- (8,0)
        to[generic,l=steel] (6,0)
        to[generic,l=Ag] (4,0)
        to[generic,l=Au] (2,0) 
        to[generic,l=W] (0,0) 
            ;
    \end{circuitikz}
    \caption{Sketch of circuit, from the source clockwise: varibale voltage source, built-in amperometer, gold plated tungsten probe, sputtered aluminium contact, \gls{zro} layer to be measured, steel substrate, dried silver paste contact, gold plated tungsten probe.}
    \label{fig:circuit}
\end{figure}
\fi

@@

The main part of all samples (200 out of 244) were pre-optimization samples, 

@@

The glass plate of the film applicator was therefore exchanged with a metal plate which

@@

%$T_{DB}$[\oc{}]
%$v_{DB}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a DB machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see table \ref{tab:pre-opt2}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Shortly before the \gls{pso} the stabilization agent was changed from \gls{acoh} to 
\gls{ipo} because of much better solution stability.
The - up to this moment - best process was chosen to be tested with 
\ml{1} \gls{acoh}, \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} and \ml{1} \gls{ipo}.
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent 
showed comparable passivization results and better stability of the solution. 
Therefore \gls{ipo} was used  as stabilzier in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, DB velocity and DB temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$\lambda$	&$v_{DB}$	&$T_{DB}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

### 2023-10-28 doc/Thesis/chapter/05-computational-details.tex
finish todos

\section{Data Processing}
\label{sec:eval}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
Multiple \gls{iv} curves were measured for every sample.
The main difficulty faced in processing the data was to present the measurements obtained 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
5 points before and 5 points after the origin with \td{at one point distance from zero} (which boils
down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
%averaging their V and I values and calculating
\begin{equation}
    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer 
%and better comparable to the 
\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$ (pin hole density), calculated in following way:
\begin{equation}
	s_i = \begin{cases}
        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

@@

\section{Fitting via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
%\subsection{Grid Search}
A grid search over a set of hyperparameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
%and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$, 
where $C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 %, $\varepsilon$ 0.05--4.0 with 0.2 steps 
\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were \td{scaled before each calculation.}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
For each calculation the 5-fold cross validation score was calculated. 
The score equals to the coefficient of determination $R^2$ which \td{ is defined the following for non linear regression functions:}
\begin{equation}
	\label{eq:r2}
	R^2 = 1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}
\end{equation}
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.
% 
Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
These values were also calculated for \gls{emma} and the linear model in order to compare the different methods.

>>>>

\section{Data Processing}
\label{sec:eval}
%Reading list
%\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
%    \item 
%\end{itemize}
%\td{describe problem and solution found}
Multiple \gls{iv} curves were measured for every sample.
The main difficulty faced in processing the data was to present the measurements obtained 
from a sample in one representative number. 
%
%\todo{why didn't i just take this?}
%\td{L2 norm because it might be easier to compare to other methods. }
%\td{inspired by euclidean norm/L2 distance from ideal case} 
%\td{wanted to put more weight on bad shunts}
%\td{plot avg, avg(log), avg(log-13)}
%
For every I-V curve (i.e.\,for every aluminium dot contact) the gradient $g$ at $V=0$ (conductance) is calculated by taking 
5 points before and 5 points after the origin with minimum one point distance from zero (which boils
down to the data points from $\pm$\SI{0.02}{\volt} to $\pm$\SI{0.07}{\volt}), 
calculating averages $\overline{V}$ and $\overline{I}$ of each point cloud and taking the ratio of differences:
%averaging their V and I values and calculating
\begin{equation}
    %g = \frac{I_{+m+d} - I_n}{V_{n+1} - V_n}.
    g = \frac{\overline{I}_{+} - \overline{I}_-}{\overline{V}_{+} - \overline{V}_-}
\end{equation}
%
The average of each conductance would be an easy and naive choice but difficult to represent a 
sample correctly since the possible values of conductance span across several magnitudes.
So the average of base 10 logarithm of conductances is the next nearby \textit{ansatz}.
%
In order to make the metric closer 
%and better comparable to the 
\gls{mse} (and to penalize deviation from ideal more than linearly) the average of the squared difference 
to the ideal non-conduction case ($g=10^{-13}$) was chosen instead of the average of logarithms and shall be called conducticity hereafter for lack of a better term. 
%As a measure of conductance a distance $D$ from an ideal non-conducting case. 
%The average of the negative base 10 logarithm subtracted from an ideal non-conducting gradient of $10^{-13}$ 
%and the mean of all conductances was taken
%
\begin{equation}
    \gamma = \sum_i^N \frac{ (-log_{10}(g_i) - 13)^2}{N}
	\label{eq:gamma}
\end{equation}
Another measure is the density of shorted species $\rho$ (pin hole density), calculated in following way:
\begin{equation}
	s_i = \begin{cases}
        1 &\text{if} \quad -log_{10}(g_i) < 5 \\
        0 &\text{if} \quad -log_{10}(g_i) \geq 5 \\
	\end{cases}
\end{equation}
\begin{equation}
	\rho = \sum_i^N \frac{s_i}{N}
	\label{eq:rho}
\end{equation}
The density is 1 if every measurement has a conductance larger than $10^{-5} \, \Omega^{-1}$ and is 0 if every measured conductance has a value of smaller than $10^{-5} \, \Omega^{-1}$.
%Other estimates of the conductance are the averages:
%\begin{equation}
%	G_1 = log \left( \sum_i^N \frac{g_i}{N} \right)
%\end{equation}
%
%\begin{equation}
%	G_2 =  \sum_i^N \frac{log(g_i)}{N}
%%\end{equation}

@@

\section{Fitting via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
%\subsection{Grid Search}
A grid search over a set of hyperparameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
%and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$. 
$C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 for \gls{svm} and \gls{krr}.
\Gls{svm} additionally used the \texttt{scale} for $\gamma_{ml}$.
%\td{and was the same as for \gls{krr} plus \texttt{scale}.} %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
\texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were scaled with the routine \texttt{sklearn.preprocessing.StandardScaler().fit\_transform()}. %\td{scaled before each calculation.}
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
For each calculation the 5-fold cross validation score was calculated. 
The score equals to the coefficient of determination $R^2$ which is defined the following for non-linear regression functions
%\footnote{see https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html\#sklearn.kernel\_ridge.KernelRidge.score}
\footnote{see \href{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}{https://scikit-learn.org/stable/modules/generated/sklearn.kernel\_ridge.KernelRidge.html}}
\begin{equation}
	\label{eq:r2}
	R^2 = 1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}
\end{equation}
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.
% 
Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
These values were also calculated for \gls{emma} and the linear model in order to compare the different methods.

### 2023-10-28 doc/Thesis/chapter/060-results-material.tex
finish todos

%Figures~\ref{fig:iv-log-good} and~\ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure~\ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
\td{Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask. }
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and around a fifth exhibit hardly any current which is ideal (see figure~\ref{fig:iv-stat-good}).
A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
The conductance (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
Figure~\ref{fig:iv-stat-good} shows the distribution of gradients $g$ for the same sample as depicted in \ref{fig:iv-log-good}.
%
Figures~\ref{fig:iv-log-okay} and~\ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures~\ref{fig:iv-log-good} and~\ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
%
This deviation (see figure~\ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
%, but was not investigated further. 
Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
%
Finally, figures~\ref{fig:iv-log-bad} and~\ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
Figure~\ref{fig:iv-ohmic} shows a \gls{iv} curve which can be approximated by Ohm's law. 
%

>>>>

%Figures~\ref{fig:iv-log-good} and~\ref{fig:iv-stat-good} are measurements from a good sample. 
%Figure~\ref{fig:iv-log-good} shows \gls{iv} curves in logarithmic scale of an insulating sample. 
Figure~\ref{fig:iv-log-good} shows \gls{iv} curves of an insulating sample, where the abscissa shows the voltage in Volt and the ordinate shows the current in Ampere. 
Each line represents a I-V measurement at a distinct aluminium contact applied by sputtering through a mask (see figure~\ref{fig:micro}).
All of the curves show a max voltage of under \num{e-6} \SI{}{\volt} 
and around a fifth exhibit hardly any current which is ideal (see figure~\ref{fig:iv-stat-good}).
A single example for a very low conductance measurement in non-logarithmic scale can be seen in figure~\ref{fig:iv-nocurrent}.
The conductance (i.e. the gradient at V=0) was calculated (see section~\ref{sec:eval}) for each measurement.
Figure~\ref{fig:iv-stat-good} shows the distribution of gradients $g$ for the same sample as depicted in \ref{fig:iv-log-good}.
%
Figures~\ref{fig:iv-log-okay} and~\ref{fig:iv-stat-okay} show measurements of a moderately insulating sample. 
Most of the \gls{iv} curves have a maximum voltage of under \num{e-6}\SI{}{\volt}, 
but there are some so called pin holes with conductance above the threshold of \num{e-5}\SI{}{\volt}. %\num{e-6} V. 
%
In figures~\ref{fig:iv-log-good} and~\ref{fig:iv-log-okay} the minimum of some curves 
is not at \SI{0}{\volt}, which means that the function does not cross the origin in non-logarithmic representation. 
%
This deviation (see figure~\ref{fig:iv-diodic}) looks similar to the deviation due to the photo-currents\cite{perez2018solar} because of its non-zero current at $V=0$.
%, but was not investigated further. 
Though, the explanation by photo-current is compelling, it does most likely not apply because of \gls{zro}'s band gap of \ev{5}\cite{sinhamahapatra2016oxygen}.
A better explanation would be the tunneling effect, whose \gls{iv} curves look very similar\cite{feenstra1994scanning,datta1997current}.
%\td{show some non log \gls{iv} curves and discuss form, some look like tunneling\cite{feenstra1994scanning,datta1997current}.}
%
Finally, figures~\ref{fig:iv-log-bad} and~\ref{fig:iv-stat-bad} show a sample 
where all measurement exhibit relatively high voltages and high calculated conductances. 
This indicates a overall bad condition of the \gls{zro} layer for insulating. 
Figure~\ref{fig:iv-ohmic} shows a \gls{iv} curve which can be approximated by Ohm's law. 
%
